---
title: "Problem 5"
author: "Shashi Bhushan Singh"
output:
  pdf_document: default
  html_document: default
editor_options:
  markdown:
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Problem 5: Computational Finance - Modelling Stock prices

Following piece of code download the prices of TCS since 2007

```{r}
library(quantmod)
getSymbols('TCS.NS')
tail(TCS.NS)
```

Plot the adjusted close prices of TCS

```{r}
plot(TCS.NS$TCS.NS.Adjusted)
```

**Download the data of market index Nifty50**. The Nifty 50 index
indicates how the over all market has done over the similar period.

```{r}
getSymbols('^NSEI')
tail(NSEI)
```

Plot the adjusted close value of Nifty50

```{r}
plot(NSEI$NSEI.Adjusted)
```

### Log-Return

We calculate the daily log-return, where log-return is defined as $$
r_t=\log(P_t)-\log(P_{t-1})=\Delta \log(P_t),
$$ where $P_t$ is the closing price of the stock on $t^{th}$ day.

```{r}
TCS_rt = diff(log(TCS.NS$TCS.NS.Adjusted))
Nifty_rt = diff(log(NSEI$NSEI.Adjusted))
retrn = cbind.xts(TCS_rt,Nifty_rt) 
retrn = na.omit(data.frame(retrn))

plot(retrn$NSEI.Adjusted,retrn$TCS.NS.Adjusted
     ,pch=20
     ,xlab='Market Return'
     ,ylab='TCS Return'
     ,xlim=c(-0.18,0.18)
     ,ylim=c(-0.18,0.18))
grid(col='grey',lty=1)
```

-   Consider the following model:

$$
r_{t}^{TCS}=\alpha + \beta r_{t}^{Nifty} + \varepsilon,
$$ where $\mathbb{E}(\varepsilon)=0$ and
$\mathbb{V}ar(\varepsilon)=\sigma^2$.

1.  Estimate the parameters of the models $\theta=(\alpha,\beta,\sigma)$
    using the method of moments type plug-in estimator discussed in the
    class.

    ```{r}
     # 1.method of moment
    y_mean=mean(retrn$TCS.NS.Adjusted)
    x_mean=mean(retrn$NSEI.Adjusted)

    xy_mean=mean(retrn$TCS.NS.Adjusted * retrn$NSEI.Adjusted)
    x2_mean=mean(retrn$NSEI.Adjusted^2)

    bet=((x_mean * y_mean)- xy_mean) / (x_mean^2 - x2_mean)

    alpha= y_mean-bet*x_mean

    sigma= sd(retrn$TCS.NS.Adjusted- alpha-bet * retrn$NSEI.Adjusted)

    print(paste("for method of moment  ","alpha :",alpha,"beta: ",bet, " sigma :",sigma))
    ```

2.  Estimate the parameters using the `lm` built-in function of `R`.
    Note that `lm` using the OLS method.

    ```{r}
    # 2. OLS
    OLS=lm(data=retrn, TCS.NS.Adjusted ~ NSEI.Adjusted)

    alpha_o= OLS$coefficients[1]
    beta_o= OLS$coefficients[2]
    sigma= sd(retrn$TCS.NS.Adjusted- alpha_o -beta_o * retrn$NSEI.Adjusted)


    print(paste("OLS  ","alpha :",alpha_o,"beta: ",beta_o," sigma :",sigma))
    ```

3.  Fill-up the following table

| Parameters | Method of Moments    | OLS                  |
|------------|----------------------|----------------------|
| $\alpha$   | 0.000462823004746492 | 0.000462823004746493 |
| $\beta$    | 0.743683986012229    | 0.74368398601223     |
| $\sigma$   | 0.0161846572261074   | 0.0161846572261074   |

4.  If the current value of Nifty is 18000 and it goes up to 18200. The
    current value of TCS is Rs. 3200/-. How much you can expect TCS
    price to go up?

    ```{r}

    Nifty_r = log(18200) - log(18000)

    TCS_r = alpha + bet * Nifty_r

    TCS_expected = exp(TCS_r + log(3200) )

    print(paste ("The expected price rise for TCS is :", TCS_expected - 3200 ))
    ```
