---
title: "Modelling Insurance Claims"
author: "**Shashi Bhushan Singh**"
date: "Submission Nov 16-2022 (Wednesday)"
output: pdf_document
editor_options: 
  markdown: 
    wrap: 72
---

## Problem 4: Modelling Insurance Claims

Consider the `Insurance` datasets in the `MASS` package. The data given
in data frame `Insurance` consist of the numbers of policyholders of an
insurance company who were exposed to risk, and the numbers of car
insurance claims made by those policyholders in the third quarter of
1973.

This data frame contains the following columns:

`District` (factor): district of residence of policyholder (1 to 4): 4
is major cities.

`Group` (an ordered factor): group of car with levels \<1 litre, 1--1.5
litre, 1.5--2 litre, \>2 litre.

`Age` (an ordered factor): the age of the insured in 4 groups labelled
\<25, 25--29, 30--35, \>35.

`Holders` : numbers of policyholders.

`Claims` : numbers of claims

```{r}
library(MASS)
plot(Insurance$Holders,Insurance$Claims
     ,xlab = 'Holders',ylab='Claims',pch=20)
grid()


```

**Note**: If you use built-in function like `lm` or any packages then no
points will be awarded.

**Part A**: We want to predict the `Claims` as function of `Holders`. So
we want to fit the following models: $$
\texttt{Claims}_i=\beta_0 + \beta_1~\texttt{Holders}_i + \varepsilon_i,~~~i=1,2,\cdots,n
$$ *Assume* : $\varepsilon_i\sim N(0,\sigma^2)$. Note that
$\beta_0,\beta_1 \in\mathbb{R}$ and $\sigma \in \mathbb{R}^{+}$.

The above model can alse be re-expressed as, $$
\texttt{Claims}_i\sim N(\mu_i,\sigma^2),~~where
$$ $$
\mu_i =\beta_0 + \beta_1~\texttt{Holders}_i + \varepsilon_i,~~~i=1,2,\cdots,n
$$

(i) Clearly write down the negative-log-likelihood function in `R`. Then
    use `optim` function to estimate MLE of
    $\theta=(\beta_0,\beta_1,\sigma)$
(ii) Calculate **Bayesian Information Criterion** (BIC) for the model.

```{r}

modelA =function(parm){
  
  l=0
  for (i in 1:nrow(Insurance)) {
    m=parm[1]+parm[2]*Insurance$Holders[i]
    l=l+dnorm(Insurance$Claims[i], mean=m, sd=exp(parm[3]), log=T) }
  
  return (-l)
}



p_A=optim(c(0,0,1),modelA)
cat("MLE : b0:", p_A$par[1], "b1:", p_A$par[2], "b3:", exp(p_A$par[3]), " ")


# Bayesian Information criterion= k*ln(n) -2 ln(L`)
BIC_A = 3 * log(nrow(Insurance)) + 2 *p_A$value

cat("BIC :", BIC_A)


```

**Part B**: Now we want to fit the same model with change in
distribution: $$
\texttt{Claims}_i=\beta_0 + \beta_1~\texttt{Holders}_i + \varepsilon_i,~~~i=1,2,\cdots,n
$$ Assume : $\varepsilon_i\sim Laplace(0,\sigma^2)$. Note that
$\beta_0,\beta_1 \in\mathbb{R}$ and $\sigma \in \mathbb{R}^{+}$.

(i) Clearly write down the negative-log-likelihood function in `R`. Then
    use `optim` function to estimate MLE of
    $\theta=(\beta_0,\beta_1,\sigma)$

<!-- -->

```{r}
dlap=function(x,m,b) {
  return( log( 1/(2*b) * exp(-abs(x-m)/b)
    
  ))
}


modelB =function(parm){
  
  l=0
  for (i in 1:nrow(Insurance)) {
    m=parm[1]+parm[2]*Insurance$Holders[i]
   l=l+dlap(Insurance$Claims[i], m, exp(parm[3]))
   
     }
  
  return (-l)
}



p_B=optim(c(0,0,1),modelB)
cat("MLE : b0:", p_B$par[1], "b1:", p_B$par[2], "b3:", exp(p_B$par[3]), " ")
BIC_B = 3 * log(nrow(Insurance)) + 2 *p_B$value

cat("BIC :", BIC_B)


```

(i) Calculate **Bayesian Information Criterion** (BIC) for the model.

**Part C**: We want to fit the following models: $$
\texttt{Claims}_i\sim LogNormal(\mu_i,\sigma^2), where
$$ $$
\mu_i=\beta_0 + \beta_1 \log(\texttt{Holders}_i), ~~i=1,2,...,n
$$

Note that $\beta_0,\beta_1 \in\mathbb{R}$ and
$\sigma \in \mathbb{R}^{+}$.

(i) Clearly write down the negative-log-likelihood function in `R`. Then
    use `optim` function to estimate MLE of
    $\theta=(\alpha,\beta,\sigma)$

(ii) Calculate **Bayesian Information Criterion** (BIC) for the model.

```{r}

Insurance1=Insurance[-61,]

modelc =function(parm){
  
  l=0
  for (i in 1:nrow(Insurance1)) {
    mu=parm[1]+parm[2]*log(Insurance1$Holders[i])
    
    
   l=l+dlnorm(Insurance1$Claims[i], meanlog=mu, sdlog= exp(parm[3]),log=T)
   
     }
  
  return (-l)
}


p_C=optim(c(2,2,1),modelc)
cat("MLE : b0:", p_C$par[1], "b1:", p_C$par[2], "b3:", exp(p_C$par[3]), " ")
BIC_C = 3 * log(nrow(Insurance1)) + 2 *p_C$value

cat("BIC :", BIC_C)


```

**Part D**: We want to fit the following models: $$
\texttt{Claims}_i\sim Gamma(\alpha_i,\sigma), where
$$ $$
log(\alpha_i)=\beta_0 + \beta_1 \log(\texttt{Holders}_i), ~~i=1,2,...,n
$$

(iii) Compare the BIC of all three models

```{r}

modeld =function(parm){
  
  l=0
  for (i in 1:nrow(Insurance1)) {
    m=exp(parm[1]+parm[2]*log(Insurance1$Holders[i]))
   l=l+dgamma(Insurance1$Claims[i], m, exp(parm[3]),log=T)
   
     }
  
  return (-l)
}

Insurance1=Insurance[-61,]

p_D=optim(c(1,1,2),modeld)
cat("MLE : b0:", p_D$par[1], "b1:", p_D$par[2], "b3:", exp(p_D$par[3]), " ")
BIC_D = 3 * log(nrow(Insurance1)) + 2 *p_D$value

cat("BIC :", BIC_D)


```

```{r}



BIC_model= data.frame("Model" = c("A","B","C","D"), "Bic_val"= c(BIC_A,BIC_B,BIC_C,BIC_D))

bst=BIC_model[BIC_model$Bic_val==min(BIC_model$Bic_val),]
print(paste("The best model is ",bst[,1], " with BIC value ", bst[,2]))



```
